---
title: "FinalAnalysisNSS"
author: "Sabine Dziemian"
date: "3/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
objects()
rm(list=ls())
options(warn=-1)

wd <- getwd()
source('/hdd/ReposPesados/SaliencyADHD/notebooks/R/readDataTable.R')
source('/hdd/ReposPesados/SaliencyADHD/notebooks/R/removeOutliers.R')
source('/hdd/ReposPesados/SaliencyADHD/notebooks/R/getOutlierList.R')
#source(paste(wd, 'calculateCohensF2.R', sep = ""))
#source(paste(wd, 'calculateCohensF2InInteraction.R', sep = ""))
```

```{r lib, include=FALSE}
library(lme4)
library(car)
library(knitr)
library(dplyr)
library(ggplot2)
#library(ggpmisc)
library(ggsignif)
library(stringr)
library(data.table)
library(fitdistrplus)
library(corrplot)

library(performance)
library(lmerTest)
#library(JWileymisc)
#library(multilevelTools)
```

# Hypotheses

H1: Overall NSS on ViNet is larger than on FineGrained regardless of group.

H2: Children with ADHD have lower NSS on FineGrained and lower NSS on ViNet than controls. 

H3: Children with ADHD show lower coherence to NSS on ViNet and than to FineGrained compared to controls.

```{r load, include=FALSE}
video <- "WK"
tablesPath <- '/Volumes/methlab/Students/Sabine Dziemian/Eye Movements in ADHD/Data/Tables/';

# averaged NSS
DAVG <- readDataTable(tablesPath, paste(video, '/FinalTableH3b', video , '.csv', sep=""))
DAVG <- removeOutliers(DAVG, video)
DAVG <- DAVG[DAVG$ADHDCategory != "OtherDx", ]
DAVG <- DAVG[DAVG$ADHDCategory != "ADHD-OS", ]
DAVG <- DAVG[DAVG$ADHDCategory != "ADHD-US", ]
DAVG <- DAVG[DAVG$ADHDCategory != "ADHD-HI", ]

DAVG$ADHDCategory <- droplevels(DAVG$ADHDCategory)
DAVG$ADHDCategory <- relevel(DAVG$ADHDCategory, ref = "NoADHD")

DAVG$ID <- as.factor(DAVG$ID)

D.fg <- DAVG
D.fg <- D.fg[ , !(names(D.fg) %in% c("NSS_vn"))]
names(D.fg)[names(D.fg) == 'NSS_fg'] <- 'NSS'
D.fg$SemLevel <- 0

D.vn <- DAVG
D.vn <- D.vn[ , !(names(D.vn) %in% c("NSS_fg"))]
names(D.vn)[names(D.vn) == 'NSS_vn'] <- 'NSS'
D.vn$SemLevel <- 1 

DF <- rbind(D.fg, D.vn)
DF$ADHDCategory <- as.factor(DF$ADHDCategory)
DF$SemLevel <- as.factor(DF$SemLevel)
```

### Correlation of NSS Values
```{r corr, echo=FALSE, fig.width=4, fig.height=3}
ggplot(DAVG, aes(x = NSS_fg, y = NSS_vn, color = SWAN_HY)) +
  geom_point()

ggplot(DAVG, aes(x = NSS_fg, y = NSS_vn, color = SWAN_IN)) +
  geom_point()

ggplot(DAVG, aes(x = NSS_fg, y = NSS_vn, color = SWAN_Total)) +
  geom_point()

ggplot(DAVG, aes(x = NSS_fg, y = NSS_vn, color = ADHDCategory)) +
  geom_point()


ggplot(DAVG, aes(x=NSS_fg, fill=ADHDCategory))+  
 geom_density(alpha=.2)+
 xlab("NSS Score (Finegrained)")+
 ylab("Frequency")+
 scale_x_continuous(n.breaks = 6)+ theme_bw() + 
 theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title = element_text(size = 16), axis.text = element_text(size = 16), legend.text = element_text(size = 16), legend.title = element_text(size = 16)) +
 scale_fill_discrete(name="Group", breaks=c("NoADHD", "ADHD-C", "ADHD-IN"), labels=c("Controls", "ADHD-C", "ADHD-IN"))

ggplot(DAVG, aes(x=NSS_vn, fill=ADHDCategory))+  
 geom_density(alpha=.2)+
 xlab("NSS Score (ViNet)")+
 ylab("Frequency")+
 scale_x_continuous(n.breaks = 6)+ theme_bw() +
 theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title = element_text(size = 16), axis.text = element_text(size = 16), legend.text = element_text(size = 16), legend.title = element_text(size = 16)) +
 scale_fill_discrete(name="Group", breaks=c("NoADHD", "ADHD-C", "ADHD-IN"), labels=c("Controls", "ADHD-C", "ADHD-IN"))
```



### Preliminary analysis of both NSS in isolation
```{r Q2avg, echo=FALSE, fig.width=4, fig.height=3}
mfg.HY <- lm(DAVG$NSS_fg ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_HY, data=DAVG, na.action = na.omit)
summary(mfg.HY)

mvn.HY <- lm(DAVG$NSS_vn ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_HY, data=DAVG, na.action = na.omit)
summary(mvn.HY)

mfg.IN <- lm(DAVG$NSS_fg ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_IN, data=DAVG, na.action = na.omit)
summary(mfg.IN)

mvn.IN <- lm(DAVG$NSS_vn ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_IN, data=DAVG, na.action = na.omit)
summary(mvn.IN)

mfg.Tot <- lm(DAVG$NSS_fg ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_Total, data=DAVG, na.action = na.omit)
summary(mfg.Tot)

mvn.Tot <- lm(DAVG$NSS_vn ~ Age + Sex + IQ + EHQ_Total + samplingRate + SWAN_Total, data=DAVG, na.action = na.omit)
summary(mvn.Tot)

mfg.cat <- lm(DAVG$NSS_fg ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory, data=DAVG, na.action = na.omit) 
summary(mfg.cat)
confint(mfg.cat)
calculateCohensF2(DAVG, "FG")
vif(mfg.cat)
plot(mfg.cat)


mvn.cat <- lm(DAVG$NSS_vn ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory, data=DAVG, na.action = na.omit) 
summary(mvn.cat)
confint(mvn.cat)
calculateCohensF2(DAVG, "VN")
vif(mvn.cat)
plot(mvn.cat)

ggplot(DAVG, aes(x=ADHDCategory, y=NSS_fg, col=ADHDCategory))+
  geom_boxplot()

ggplot(DAVG, aes(x=ADHDCategory, y=NSS_vn, col=ADHDCategory))+
  geom_boxplot()
```

## Main Analysis

#### Model Definition

NSS ~ Age + Gender + IQ + Handedness + Sampling Rate + SWAN * Semantic Level + (1|ID)

```{r modelQ4avgHY}
m.cat <- lmer(NSS ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory * SemLevel + (1|ID), data=DF, na.action = na.omit) 

# choose model m2.cat
vif(m.cat)
check_collinearity(m.cat)
summary(m.cat)
confint(m.cat)
calculateCohensF2InInteraction(DF)
```

## Additional Confirmatory Analysis

### Bootstrap with z-transformed NSS 
```{r boot}

iterations <- 1000

b.fg <- rep(NA, iterations)
b.vn <- rep(NA, iterations)

for (i in 1:iterations){
  D.frac <- DAVG %>% sample_frac(.8)

  m.fg <- lm(D.frac$NSS_fg ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory, data=D.frac, na.action = na.omit) 
  m.vn <- lm(D.frac$NSS_vn ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory, data=D.frac, na.action = na.omit) 
  
  b.fg[i] <- m.fg$coefficients[8]
  b.vn[i] <- m.vn$coefficients[8]
}


df <- data.frame(
  Map=factor(rep(c("Finegrained", "ViNet"), each=1000)),
  beta= c(b.fg, b.vn))

ggplot(df, aes(x=beta, fill=Map, color=Map)) +
  geom_histogram(alpha=0.5, position="identity")+
  xlab("Estimate")+ ylab("Count")+
  theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) 


hist(b.vn)
hist(b.fg)
summary(b.vn)
summary(b.fg)

t.test(b.vn, b.fg)

t.test(b.vn, b.fg, alternative = c("less"), paired = FALSE, var.equal = TRUE)
wilcox.test(b.vn, b.fg, alternative = c("less"), paired = FALSE, var.equal = FALSE)
```



### Add-on check for collinearity in interaction model
```{r boot}

iterations <- 1000

b.adhdc <- rep(NA, iterations)
b.adhdin <- rep(NA, iterations)
b.sem <- rep(NA, iterations)
b.intc <- rep(NA, iterations)
b.intin <- rep(NA, iterations)

bo.adhdc <- rep(NA, iterations)
bo.adhdin <- rep(NA, iterations)
bo.sem <- rep(NA, iterations)

for (i in 1:iterations){
  D.frac <- DF %>% sample_frac(.8)
  
  # with interaction
  m <- summary(lmer(D.frac$NSS ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory * SemLevel + (1|ID), data=D.frac, na.action = na.omit))

  b.adhdc[i] <- m$coefficients[8]
  b.adhdin[i] <- m$coefficients[9]
  b.sem[i] <- m$coefficients[10]
  b.intc[i] <- m$coefficients[11]
  b.intin[i] <- m$coefficients[12]
  
  # without interaction
  mo <- summary(lmer(D.frac$NSS ~ Age + Sex + IQ + EHQ_Total + samplingRate + ADHDCategory + SemLevel + (1|ID), data=D.frac, na.action = na.omit))

  bo.adhdc[i] <- mo$coefficients[8]
  bo.adhdin[i] <- mo$coefficients[9]
  bo.sem[i] <- mo$coefficients[10]
}

# with interaction
hist(b.adhdc)
hist(b.adhdin)
hist(b.sem)
hist(b.intc)
hist(b.intin)

df <- data.frame(b.adhdc, b.adhdin, b.sem, b.intc, b.intin)
pairs(df)

# without interaction
hist(bo.adhdc)
hist(bo.adhdin)
hist(bo.sem)

dfo <- data.frame(b.adhdc, b.adhdin, b.sem, b.intc, b.intin)
pairs(dfo)
```








